\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-11-15 papers/jss/article.Rnw
Make section 3 a little more concise and address referee feedback by not having so many small subsections, only using one style and sticking to it in this section, and not talking about ill defined 'pseudo-methods'.
Sorry I didn't build this yet about to go home wanted to easily
capture some edits on work computer.  hopefully it doesn't break the
build. will be easy to fix if i did.



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@898 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\subsection[Importing message descriptors from .proto files]{Importing message descriptors from \code{.proto} files}

@@

<<>>=
ls("RProtoBuf:DescriptorPool")
@

\subsection{Creating a message}

@@

<<>>=
p1 <- new(tutorial.Person)
p <- new(tutorial.Person, name = "Murray", id = 1)
@

\subsection{Access and modify fields of a message}

@@

\subsection{Display messages}

@@

\subsection{Serializing messages}

@@

\code{serialize} can also be called in a more traditional
object oriented fashion using the dollar operator.

<<>>=
p$serialize(tf1)
con <- file(tf2, open = "wb")
p$serialize(con)
close(con)
@

Here, we first serialize to a file \code{tf1} before we serialize to a binary
connection to file \code{tf2}.

\subsection{Parsing messages}

@@

\code{read} can also be used as a pseudo-method of the descriptor
object:

<<>>=
message <- tutorial.Person$read(tf1)
con <- file(tf2, open = "rb")
message <- tutorial.Person$read(con)
close(con)
message <- tutorial.Person$read(payload)
@

Here we read first from a file, then from a binary connection and lastly from
a message payload.

>>>>

% Note: We comment out subsections in favor of textbf blocks to save
% space and shrink down this section a little bit.
%\subsection[Importing message descriptors from .proto files]{Importing message descriptors from \code{.proto} files}

\textbf{Importing message descriptors from \code{.proto} files}

@@

% Commented out for now because its too detailed.  Lets shorten
% section 3 per referee feedback.

<<echo=FALSE,print=FALSE>>=
ls("RProtoBuf:DescriptorPool")
@

% \subsection{Creating a message}
\textbf{Creating, accessing, and modifying a message.}

@@

<<>>=
p <- new(tutorial.Person, name = "Murray", id = 1)
@

%\subsection{Access and modify fields of a message}

@@

%\subsection{Display messages}
\textbf{Printing, Reading, and Writing Messages}

@@

% \subsection{Serializing messages}

@@

% TODO(mstokely): commentd out per referee feedback, but see if this is
% covered in the package documentation well.
%
%\code{serialize} can also be called in a more traditional
%object oriented fashion using the dollar operator.
%
%<<>>=
%p$serialize(tf1)
%con <- file(tf2, open = "wb")
%p$serialize(con)
%close(con)
%@
%
%Here, we first serialize to a file \code{tf1} before we serialize to a binary
%connection to file \code{tf2}.

%\subsection{Parsing messages}

@@

% TODO(mstokely): comment out and use only one style, not both per
% referee feedback.  Also avoid using the term 'pseudo-method' which
% is unclear.
%
%\code{read} can also be used as a pseudo-method of the descriptor
%object:
%
%<<>>=
%message <- tutorial.Person$read(tf1)
%con <- file(tf2, open = "rb")
%message <- tutorial.Person$read(con)
%close(con)
%message <- tutorial.Person$read(payload)
%@
%
%Here we read first from a file, then from a binary connection and lastly from
%a message payload.
